Adaptive group-regularized logistic elastic net regression Supplementary material

### 2019-03-08 docs/supplement.Rnw
parallelised simulations.R simulation 1

  \subsection{Stability of selection}
  One common criticism on the elastic net, and especially the lasso, is the 
  instability of feature selection. That is, different data sets yield different
  sets of selected features. To investigate the stability of feature selection 
  by \texttt{gren} we created 50 stratified bootstrap samples from the microRNA 
  data \cite[]{neerincx_combination_2018}, where we stratified by the target of 
  prediction, treatment response. 
  For each of these bootstrap samples we estimated the regular elastic
  net and \texttt{gren} for $\alpha \in \{0.05, 0.5, 0.95 \}$, where we selected
  25 features (including the 5 unpenalized covariates). We calculated the size 
  of all $\genfrac(){0pt}{2}{50}{2}$ intersections of selected features and
  present the results in Figure [! figure ref here].

  [! figure here]

>>>>

  \subsection{Stability of selection}
  One common criticism on the elastic net, and especially the lasso, is the 
  instability of feature selection. That is, different data sets yield different
  sets of selected features. To investigate the stability of feature selection 
  by \texttt{gren} we created 50 stratified bootstrap samples from the microRNA 
  data \cite[]{neerincx_combination_2018}, where we stratified by the target of 
  prediction, treatment response. 
  For each of these bootstrap samples we estimated the regular elastic
  net and \texttt{gren} for $\alpha \in \{0.05, 0.5, 0.95 \}$, where we selected
  25 features (including the 5 unpenalized covariates). We calculated the size 
  of all $\genfrac(){0pt}{2}{50}{2}$ intersections of selected features and
  present the results in Figure 
  \ref{fig:hist_micrornaseq_colorectal_cancer_res4_overlap}.
<<hist_micrornaseq_colorectal_cancer_res4_overlap, fig.cap="Stability of feature selection in colorectal cancer example for (a) $\\alpha=0.05$, (b) $\\alpha=0.5$, and (c) $\\alpha=0.95$.", out.width="100%", fig.asp=2/3>>=
@
